---
title: "國際生問卷初步分析一"
author: "Russ"
date: "8/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Survey participants with high and low knowledge scores     
&nbsp;                      
&nbsp;     
&nbsp;        

```{r cars, echo=FALSE}
library(dplyr)
library(gtsummary)
Table1 <- int_students_total %>%
  filter(knowledge_total < 4) %>%
  select(gender,
         age,
         country_origin2,
         chinese_lang,
         religion_attendance,
         religion, university2,
         survey_round,
         education_level,
         health_background, 
         months_in_taiwan, 
         info_source_socialmedia,
         info_source_newspaper,
         info_source_online,
         info_source_friends)  %>% 
  tbl_summary() 

table2 <- int_students_total %>%
  filter(knowledge_total > 5) %>%
  select(gender,
         age,
         country_origin2,
         chinese_lang,
         religion_attendance,
         religion, university2,
         survey_round,
         education_level,
         health_background, 
         months_in_taiwan, 
         info_source_socialmedia,
         info_source_newspaper,
         info_source_online,
         info_source_friends) %>% 
  tbl_summary()

table3 <- tbl_merge(
  tbls = list(Table1, table2), 
    tab_spanner = c("**Low knowledge </= 3**", "**High Knowledge >/= 6**"))

table3
#%>%
  # as_gt(include = -cols_align) %>%
  #gt::tab_source_note(gt::md("**"))


```

# Round 3 only
Here's the same table repeated for ***only*** the third survey round

&nbsp;                      
&nbsp;     
&nbsp;        

```{r cars dua, echo=FALSE}
library(dplyr)
library(gtsummary)
Table1 <- int_students_total %>%
  filter(survey_round=="round_3") %>%
  filter(knowledge_total < 4) %>%
  select(gender,
         age,
         country_origin2,
         chinese_lang,
         religion_attendance,
         religion, university2,
         survey_round,
         education_level,
         health_background, 
         months_in_taiwan, 
         info_source_socialmedia,
         info_source_newspaper,
         info_source_online,
         info_source_friends)  %>% 
  tbl_summary() 

table2 <- int_students_total %>%
  filter(survey_round=="round_3") %>%
  filter(knowledge_total > 5) %>%
  select(gender,
         age,
         country_origin2,
         chinese_lang,
         religion_attendance,
         religion, university2,
         survey_round,
         education_level,
         health_background, 
         months_in_taiwan, 
         info_source_socialmedia,
         info_source_newspaper,
         info_source_online,
         info_source_friends) %>% 
  tbl_summary()

table3 <- tbl_merge(
  tbls = list(Table1, table2), 
    tab_spanner = c("**Low knowledge </= 3**", "**High Knowledge >/= 6**"))

table3
#%>%
  # as_gt(include = -cols_align) %>%
  #gt::tab_source_note(gt::md("**"))


```

&nbsp;                      
&nbsp;     
&nbsp; 
&nbsp;                      
&nbsp;     
&nbsp; 

## Why was 6 the cut off for high knowledge?
Here are the total number of people who answered each knowledge question correctly          

```{r confusing, echo=FALSE}
int_students_total %>% 
  dplyr::select(opn_feverless_transm_yesno:knowledge_present)%>% 
  colSums()

```
         
         opn_onlycough_transm_yesno = Please select a proper perception toward the following questions    SARS CoV 2  Virus causing COVID 19  spreads through respiratory droplets only when infected people cough and sneeze         

Looks like the question about coughing may have confused people....      

&nbsp;                      
&nbsp;     
&nbsp; 
&nbsp;                      
&nbsp;     
&nbsp;          


## Why was 3 the cut off for low knowledge?
- Because we want to know who *really* doesn't get it 
- And not accidentally include people who misread a question or two
&nbsp;                      
&nbsp;     
&nbsp; 
&nbsp;                      
&nbsp;     
&nbsp; 
&nbsp;                      
&nbsp;     
&nbsp;
