---
title: "Variable cleaning proposals"
author: "Russ"
date: "8/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load packages, include=FALSE}
require(tibble)
require(knitr)
require(kableExtra)
```
## R Markdown

Here are:             

  - variables we can consider removing 
  - responses that we can consider combining
  

## Removals

### hist_contactw14days_type

Have you been in contact with someone who came to Taiwan in the last two weeks? 

Here are the range or responses, so I propose we eliminate this column without further analysis

```{r satu, echo=FALSE}

kable(table(int_students_total$hist_contactw14days_type,useNA = "ifany"))


```

### hist_twtravel_locations 

```{r satu punto dua, echo=FALSE}

kable(table(int_students_total$hist_twtravel_locations,useNA = "ifany"))


```
          
&nbsp;                           
&nbsp;          

Not sure what we learn from this....


## Combine entries


### opn_country_highrisk_other


Range of responses:

```{r dua, echo=FALSE}

kable(table(int_students_total$opn_country_highrisk_other,useNA = "ifany"))

```
          
&nbsp;                           
&nbsp;          
&nbsp;         
                 


Possible fixes:

  1. Combine all I don't know variations
  2. Combine all everywhere variations + don't travel
  3. Easy stuff: make newzealand new zealand etc. 
  
            
&nbsp;                           
&nbsp;          
&nbsp;  
  
### opn_country_lowrisk_other
  
Range of responses:

```{r tiga, echo=FALSE}

kable(table(int_students_total$opn_country_lowrisk_other,useNA = "ifany"))

```
          
&nbsp;                           
&nbsp;          
&nbsp;  

Possible fixes:

  1. Combine all I don't know variations
  2. Combine all everywhere variations + don't travel
  3. Easy stuff: make newzealand new zealand etc. 
          
&nbsp;                           
&nbsp;          
&nbsp;  

### opn_infosource_worst_other


Range of responses:

```{r empat}

kable(table(int_students_total$opn_infosource_worst_other,useNA = "ifany"))

```

&nbsp;                      
&nbsp;     
&nbsp;

Possible fixes:

1. Combine all social media responses
2. combine (non-expert) friends/family responses
